\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}

\geometry{left=0.75in, right=0.75in, top=1in, bottom=1in}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

\begin{document}

\begin{center}
    {\LARGE \textbf{Chitrathep Chitranuwatkul}} \\
    Software Developer \\
    Bangkok City, Thailand \\
    \href{mailto:chitrathep.ic3@outlook.com}{chitrathep.ic3@outlook.com} \\
    \href{https://www.linkedin.com/in/ic3-chitrathep}{www.linkedin.com/in/ic3-chitrathep} \\
    Tel: 099-820-1832 \\
\end{center}

\vspace{1em}

\section*{Summary}
As a passionate software engineer with 6 years of experience, I possess a strong foundation in software design, development, and testing. I am now seeking an opportunity that will allow me to further grow and utilize my expertise in software development. My goal is to contribute to meaningful projects that make a positive impact on people's lives. Let's collaborate to make software that truly makes a difference.

\section*{Experience}

\subsection*{Lansing Business Systems Co. Ltd. \hfill Bangkok City, Thailand}
\subsubsection*{Software Developer \hfill May 2023 – Present}
\begin{itemize}[leftmargin=1.5em]
    \item Software Developer onsite at Krungsri Auto
    \item Developed a mobile application using Flutter together with native apps on Android and iOS.
    \item Built a backend system using a serverless framework that uses Python and Golang.
    \item Developed a web-based CMS system using Vue.js to assist internal users.
    \item Created infrastructure on AWS using Terraform.
\end{itemize}

\subsection*{Satang Technology Co., Ltd \hfill Bangkok, Bangkok City, Thailand}
\subsubsection*{Software Developer \hfill October 2021 – April 2023}
\begin{itemize}[leftmargin=1.5em]
    \item Developed systems that connect to the blockchain, such as faucets, explorers, and SDKs.
    \item Worked on projects integrating blockchain technology into web and mobile applications.
    \item Knowledge of smart contracts and experience using tools such as Solidity and Truffle to write and deploy them.
\end{itemize}

\subsection*{CODIUM \hfill June 2019 – October 2021}
\subsubsection*{Software Developer}
\begin{itemize}[leftmargin=1.5em]
    \item Designed and implemented scalable backend systems using Python and Django REST.
    \item Created service backoffices for companies transitioning from paper-based systems to digital ones.
    \item Designed APIs and created efficient data processing systems to streamline operations and improve efficiency.
\end{itemize}

\subsection*{Thai Embedded Systems Association \hfill January 2019}
\subsubsection*{Software Developer}
\begin{itemize}[leftmargin=1.5em]
    \item Developed servers and connected them with various applications and sensors using Node.js.
    \item Connected servers with the Line application using the Line Messaging API to create bots for messaging and actions.
\end{itemize}

\subsection*{KASIKORN Business-Technology Group [KBTG] \hfill June 2018 – July 2018}
\subsubsection*{Software Developer Intern}
\begin{itemize}[leftmargin=1.5em]
    \item Worked with blockchain technology and Stellar.
    \item Developed backend systems using Node.js that connect to blockchain networks.
\end{itemize}

\section*{Education}

\subsection*{Thammasat University \hfill (2015 – 2019)}
\subsubsection*{Bachelor's degree, Computer Engineering}

\section*{Skills}
Golang, Python, Flutter, Node.js (Typescript), AWS, Terraform, Docker, Git, Django, Agile, TDD

\section*{Certifications}
\begin{itemize}[leftmargin=1.5em]
    \item \href{https://www.skooldio.com/certificate/2876a405-cb34-41de-9284-f8fe3ac85786}{Software Architecture Design}
    \item \href{https://www.skooldio.com/certificate/a80cacde-61aa-4d34-8c49-3394668b3a30}{Tactical Domain Driven Design}
    \item \href{https://www.skooldio.com/certificate/7b01976d-6aef-4985-8392-2954ab70928c}{Go: The Fundamentals}
    \item \href{https://refactoring.guru/cert/r/MTM5Njkx}{Dive Into Refactoring}
    \item \href{https://certificate.skilllane.com/certificates/E9YB924}{Ethereum Developer Zero to Hero}
\end{itemize}

\section*{Honors-Awards}
Top score on server programming

\end{document}
